Multiple Dice Working as One: CAD Flows and Routing Architectures for Silicon Interposer FPGAs

### 2014-12-16 doc/journal/fpgapaperfinal/FPGAPaper/fpga2014paper.tex
Adding critical path graph for 4 partitions.
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4541 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Adding reference to Metis manual, removing done TODOs
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4543 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Updating reference for packing constraints
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/svn/branches/javeed@4547 8e3573b8-cf2c-4f14-ef6d-137439e28b8b
Adding double line to geomean in table
git-svn-id: https://vtr-verilog-to-routing.googlecode.com/s

\usepackage[cmex10]{amsmath}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{enumitem}
\usepackage{cite}

@@

%   - Impact of # of cutlines
\subsection{Impact of Number of Dice}
\label{num_dice_impact}
To examine the impact of the number of dice used to construct an interposer-based FPGA, we compare the minimum channel width for FPGA systems composed of four dice and two dice, respectively, while varying the fraction of wires cut at the interposer boundaries. We used the best CAD flow from Section \ref{sec:partitioner_stage_results} and the same interposer routing architecture parameters as Section \ref{sec:resultsWiringCapacity}. 
As Figure \ref{fig:wires_cut_4part} shows, four-die systems perform almost as well in routability as two-die systems until the \textit{\% wires cut} exceeds 80\%, at which point routability is worse for the four-die system. 
TODO JAVEED -- add extra line to graph, make sure same circuits for all points.

@@

Systems with more dice are slower; on average the critical path delay is xx\% higher for a four-die system than a two-die system. This speed difference is not significantly affected by the \textit{\% wires cut}.
 TODO JAVEED -- figure out critical path delay %.

@@

\begin{figure}[!htbp]
\centering
\subfigure[]{\includegraphics[height = 5cm]{square_fpga.pdf}}
\subfigure[]{\includegraphics[height = 9.335cm]{tall_fpga.pdf}}
\caption{Devices with (a) a square interposer and (b) square dice.}
\label{fig:square_tall}
\end{figure}

\begin{table}[!htbp]
\centering
\begin{tabular}{|l|r|r|}
\hline
 & Square Interposer & Square Dice \\ \hline \hline
bgm & 102 & 306 \\ \hline
stereovision0 & 86 & 256 \\ \hline
stereovision1 & 166 & 256 \\ \hline
LU8PEEng & 156 & 126 \\ \hline
mkDelayWorker32B & 96 & 194 \\ \hline
mcml & 196 & 496 \\ \hline
LU32PEEng & 256 & 264 \\ \hline
geomean & 141 & 252 \\ \hline
\end{tabular}
\caption{Minimum channel width for square interposer and square dice configurations.}
\label{table:squares}
\end{table}

>>>>

\usepackage[cmex10]{amsmath}
\usepackage{graphicx}
\usepackage{mathtools}
\usepackage{subfigure}
\usepackage{epstopdf}
\usepackage{enumitem}
\usepackage{cite}
\usepackage{hhline}

@@

%   - Impact of # of cutlines
\subsection{Impact of Number of Dice}
\label{num_dice_impact}
To examine the impact of the number of dice used to construct an interposer-based FPGA, we compare the minimum channel width for FPGA systems composed of four dice and two dice, respectively, while varying the fraction of wires cut at the interposer boundaries. We used the best CAD flow from Section \ref{sec:partitioner_stage_results} and the same interposer routing architecture parameters as Section \ref{sec:resultsWiringCapacity}. 
As Figure \ref{fig:wires_cut_4part} shows, four-die systems perform almost as well in routability as two-die systems until the \textit{\% wires cut} exceeds 80\%, at which point routability is worse for the four-die system.

@@

Systems with more dice are slower; on average the critical path delay is xx\% higher for a four-die system than a two-die system. This speed difference is not significantly affected by the \textit{\% wires cut}.
\begin{figure}[!htbp]
\centering
\input{crit_path_4part}
\caption{Impact of number of dice on critical path delay. TODO JAVEED -- LU32 90\% result is missing}
\label{fig:crit_path_4part}
\end{figure}

@@

\begin{figure}[!htbp]
\centering
\subfigure[]{\includegraphics[height = 3cm]{square_fpga.pdf}}
\subfigure[]{\includegraphics[height = 4.6675cm]{tall_fpga.pdf}}
\caption{Devices with (a) a square interposer and (b) square dice.}
\label{fig:square_tall}
\end{figure}

\begin{table}[!htbp]
\centering
\begin{tabular}{|l|r|r|}
\hline
 & Square Interposer & Square Dice \\ \hline \hline
bgm & 102 & 306 \\ \hline
stereovision0 & 86 & 256 \\ \hline
stereovision1 & 166 & 256 \\ \hline
LU8PEEng & 156 & 126 \\ \hline
mkDelayWorker32B & 96 & 194 \\ \hline
mcml & 196 & 496 \\ \hline
LU32PEEng & 256 & 264 \\ \hhline{|=|=|=|}
geomean & 141 & 252 \\ \hline
\end{tabular}
\caption{Minimum channel width for square interposer and square dice configurations.}
\label{table:squares}
\end{table}
